Robot Grasping in Clutter:\\ Using a Hierarchy of Supervisors for Learning from Demonstrations

### 2016-04-29 paper.tex
added figs

\title{Robotic Grasping in Clutter: Using a Hierarchy of Supervisors with Learning from Demonstrations}

\author{Michael Laskey$^1$, Jonathan Lee$^1$, Caleb Chuck$^1$, David Gealy$^1$, Wesley Hsieh$^1$, Florian T. Pokorny,\\
 Anca D. Dragan$^1$, and Ken Goldberg$^{1,2}$% <-this % stops a space
\thanks{$^1$ Department of Electrical Engineering and Computer Sciences; {\small \{mdlaskey,iamwesleyhsieh,ftpokorny,anca\}@berkeley.edu} }%
\thanks{$^2$ Department of Industrial Engineering and Operations Research; {\small goldberg@berkeley.edu}}%
\thanks{$^{1-2}$ University of California, Berkeley;  Berkeley, CA 94720, USA}%
}
\begin{document}

@@

\begin{abstract}
For applications such as Amazon warehouse order fulfillment, robots must grasp a desired object amid clutter: other
objects that block direct access.  This can be difficult to program explicitly due to uncertainty in friction and push
mechanics and the large number of objects that can be encountered. Online Learning from Demonstration (LfD) algorithms
such as DAgger and SHIV have potential to learn robot control policies for tasks where the system dynamics and the cost
function are unknown. To reduce the burden on human experts to provide control demonstrations, we propose using a
hierarchy of supervisors and a Deep Learning network to learn a grasping in clutter task.  We consider 3 levels of
supervisors, a fast motion planner that ignores obstacles, crowdsourced human workers who
provide appropriate robot control values via online videos, and local human experts.  Experiments suggest that we can
leverage a hiearchy of supervisors to obtain 22,000 labeled training data examples and achieve 80\% success on a held out test set of cluttered object configurations that contain objects not trained on.

@@

\section{Introduction} 
As illustrated by the recent Amazon Picking Challenge at ICRA 2015, the grasping in clutter problem, where a robot needs
to grasp an object that might be occluded by other objects in the environment poses an interesting challenge to robotic
systems. This problem is relevant to industrial applications such as warehouse shipping operations and flexible manufacturing in a semi-structured environments. One fundamental approach to grasping in clutter is the analytic model driven approach~\cite{bicchi2000robotic},
where the interaction dynamics between the robot and obstacles are formulated analytically. However, modeling all the 
physical properties of interaction poses a highly challenging problem due to uncertainty in modeling parameters such as
inertial properties and friction.

@@

\begin{figure}
\includegraphics[width=0.5\textwidth]{f_figs/teaser.eps}
\caption{
    \footnotesize
Three policy roll-outs on a Zymark 3-DOF Robot of a fully trained grasping in clutter policy (one per column, top to
bottom) which was trained using a hierarchy of three supervisors consisting of a motion planning algorithm, crowd-sourcing and a human expert. 
Red shapes indicate clutter objects and the robot is trained to reach the yellow cylinder. The trained manipulation
policy is represented as a deep neural network that recieves as input an image of the scene and outputs a change in
state position. The resulting policy learns to sweep away clutter objects to reach the goal object. }
\vspace*{-20pt}
\label{fig:teaser}
\end{figure}

@@

Our approach is based on Online Learning from Demonstrations where a robot iteratively learns a policy and is
provided feedback on the current policy roll out by a supervisor~\cite{grollman2007dogged,ross2010efficient,ross2010reduction}. 
We build on, DAgger, an online LfD algorithm which at each iteration, computes a policy based on prior demonstrations,
and then rolls out that policy. A supervisor then provides control signals as feedback on the current policy
and new state/control examples are aggregated with the prior examples for the next iteration. DAgger and related algorithms have been applied in a wide range of applications, from quadrotor flight to natural language to Atari games~\cite{NIPS2014_5421,duvallet2013imitation,ross2013learning}. 
Ross et al. showed that DAgger, under a no-regret assumption, can be guaranteed to deviate from the supervisor's policy with an error
at most linear in the time horizon for the task~\cite{ross2010reduction}.

One drawback is that DAgger imposes a substantial burden on the supervisor, who must label all states that the robot
visits during training.  Previously a single expert supervisor has been considered 
~\cite{ross2010efficient,ross2010reduction,ross2013learning,duvallet2013imitation}.

In this work, we propose to instead
utilize a hierarchy of supervisors that exhibit increasing cost and competence at a given task to incrementally
bootstrap the learning process. In particular, while model-based planners might not capture physical interactions with
complete realism. We propose to leverage model-based planners in the initial training phase rather than to utilize an expensive
expert supervisor from scratch. Thus, at the lowest level of the hierarchy, we use a motion planner on an simplified
version of the grasping in clutter problem that ignores ambient obstacles. As the next supervisor in the hierarchy, 
we consider crowdsourced workers on Amazon Mechanical Turk and finally the robot is trained with a Phd student in
robotics, who is considered an expert human supervisor. When trained with the full hierarchy the robot is able to achieve an 80\% success rate on 20 configurations that each contain new objects. Examples of the resulting learned grasping in clutter policy can be seen in Fig. \ref{fig:teaser}.

%Learning can be bootstrapped with a sequence of increasingly skilled supervisors. In our grasping in clutter example, the robot spends a large portion of the time learning how to go towards the goal object. Analytical techniques such as forward kinematics, template matching and motion planning are readily available to provide examples in these parts of the state space.

@@

\section{Related Work}
Below, we summarize related work in Robotic Grasiping in Clutter, the Online LfD setting and Curriculum learning.

\noindent \textbf{Robotic Grasping in Clutter}
Robotic grasping is a well-established research topic in robotics that has been studied for several
decades~\cite{bicchi2000robotic}. A significant amount of prior work focuses on planning grasps given a known object.
However, in unstructured environments clutter poses a significant challenge for reaching the planned grasp
~\cite{katz2008can}. Prior work has addressed integrated perception and grasping in clutter where the objective is to
grasp objects in an unorganized pile~\cite{pinto2015supersizing,nieuwenhuisen2013mobile}, but these methods do not
specifically aim to grasp a single target object in clutter. 
Prior work has studied the problem of manipulating objects
by performing pushing operations~\cite{mason1986mechanics}.  Cosgun et al.~\cite{cosgun2011push} and King et al. \cite{kingnonprehensile} consider the problem of planning a series of push operations that move an object to a
desired target location. Kiteav et al. planned a trajectory in a physics simulator using LQG based controllers
\cite{kitaevphysics}. However, all of these works assume known properties of the object model, such as mass and friction
coefficient  or access to an object model in a physics simulator, which can be difficult to obtain for unknown objects. 
Leeper et al. ~\cite{leeper2012strategies} used a human operator for assistance
to guide the robot through clutter with the objective of grasping a target object. However, the robot required the human
to be present at all times and did not attempt to learn to operate autonomously. We are interested in a data-driven
approach that only queries a supervisor at training time and  can operate autonomously thereafter.

A model-free approach to robotic manipulation is Guided Policy Search~\cite{levine2015end}. However, this assumes a
known low-dimensional state representation to both estimate dynamics and perform LQG in. In the grasping in clutter
domain, it can be hard to specify such a low dimensional representation due the dependence on the objects' shape.

@@

\noindent\textbf{Reducing Supervisor Burden in Online LfD} 
Active learning approaches to reducing supervisor burden only ask for supervision when the robot is uncertain about the
correct control to apply. Traditional active learning techniques like query-by-committee and uncertainty sampling have
been utilized for this purpose \cite{chernova2009interactive,judah2011active,grollman2007dogged}
Kim et al. demonstrated that due to the non-stationarity of the distribution of states encountered during
learning, the traditional active learning techniques may not be suitable.
Thus the use of novelty detection was proposed~\cite{kim2013maximum}. Laskey et al. introduced SHIV, using an active
learning approach tailored to high dimensional and non-stationarity state distributions and a modified version of the
One Class SVM classifier. This reduced the density estimation problem to a 
simpler regularized binary classification~\cite{laskeyshiv}. However the grasping in clutter problem exhibits a high amount
of variability in parameters requiring a large training data set. This poses a significant computational challenge to these methods.
In the present paper, we hence consider using Deep Learning, as a scalable learning algorithm in combination
with DAgger.

@@

\section{Problem Statement}
Given a collection of increasingly able and costly supervisors $S_1, \ldots, S_M$, the goal of this work is to learn a
policy that closely matches that of the most able supervisor $S_M$ while minimizing the overall cost of training a
policy. We formalize this approach as follows.

\noindent\textbf{Assumptions and Modeling Choices } 
We assume a known state space and set of controls. We also assume access to a robot or simulator, such that we can sample from the state sequences induced by a sequence of controls. Lastly, we assume access to a set of supervisors who can, given a state, provide a control signal label. We additionally assume the supervisors can be noisy and imperfect, noting that a lower cost supervisor also has lower quality.

@@

This sub-problem is a supervised learning problem, which we solve with a deep neural network. Other approaches such as
support vector machines can also be considered~\cite{scholkopf2002learning}.

@@

\section{Robot Grasping in Clutter}\label{sec:sys}
Let us now describe how we apply the above approach for the grasping in clutter problem. We consider a robot grasping an
object in a cluttered environment. The robot's goal is to grasp a yellow cylindrical target object while other extruded
planar objects obstruct the path towards the goal object. Since contact dynamics are difficult to model \cite{kitaevphysics,kingnonprehensile}, we do not assume the knowledge of explicit object or dynamics models and instead learn a grasping policy directly from labeled
overhead video data. The state space space $\mathcal{X}$, is hence given by an image from an overhead video
camera, observing a set of K objects, the robot arm and a goal object in a bounded workspace. $U$ denotes the set of continuous control
signals given by delta values of joint angles, we consider control of the robots arm extension, base rotation and gripper, as shown in \ref{fig:robot}. We consider the following three supervisors $S_1, S_2, S_3$, which try to optimize the underlying reward
function of $1$ if a trajectory ends with the goal object in the gripper and $0$ otherwise.

\noindent \textbf{Motion Planner Ignoring Obstacle Supervisor} Our first supervisor, $S_1$, is a first order motion planner that computes
control signals for the robot to reach the goal object in a straight line, ignoring the presence of obstacles. We refer to this supervisor as a Motion Planner  Ignoring Obstacles (MPIO). Our
method employs template matching to identify the goal object in the image and uses the forward dynamics of the robot to
compute the relative change in direction the robot should apply as a control. The template matching is implemented in
OpenCV and uses the normalized cross-correlation filter~\cite{opencv_library}. This supervisor is intentionally
simplistic to execute and implement, and is designed to just provide an initial improvement of a random neural network policy.
We assign a cost of $C_1 = \$0.01$ to this supervisor, which stems from the amtorized cost need to implement this supervisor. This cost is set as an example of what one could consider. 
\begin{figure}[t]
\centering

\caption{\footnotesize  The interface AMT workers see for providing feedback to the robot for the grasping in clutter task. The pink overlay indicates the desire change in the robot position with respect to the current robot state. Then AMT workers can use their intuition for how objects respond to force to provide examples of how the robot should behave. On the left side is an example of a robot state and on the right side is an example a human supervisor would provide via a Computer Mouse.}
\vspace*{-10pt}
\label{fig:overlays}
\end{figure}

\noindent \textbf{Crowd-Sourced Supervisor} The second supervisor, $S_2$, relies on a crowd source service, called Amazon
Mechanical Turk (AMT). The AMT platform makes readily available thousands of human workers that we can query to provide robot
supervision examples for approximately \$0.10 per robot trial. We use as an example cost $C_2 = 0.1$, which is based on the crowdsource pay rate. 
We designed the supervision interface shown in Fig. \ref{fig:overlays}. The interface displays a video of a roll-out of
the current robot policy and allows the human supervisors to command an overlay visualization of the robot arm to
showcase a deviation to the current policy that should be applied with a maximal angle joint deviation of 15 degree and maximal extension deviation of 1cm  to
the current roll-out.

We additionally designed a tutorial for the Crowd-Sourced Supervisor. We first describe the learning task to them as a
robot that is trying to reach a yellow cylinder and needs their help learning how to get it. In a tutorial, they are then trained
to perform designated motions with a virtual robot, to help them understand how the robot's kinematics. We additionally
provide a video of an expert providing corrections on three robot trajectories. We lastly instruct the Crowd-Sourced
Supervisor to only label when they are sure in their decision, in order to minimize contradictory examples associated
with random guesses.

To help ensure quality, we provide all Crowd-Sourced Supervisors with the same robot trial first and measure their
performance against the performance of a Human Expert Supervisor. If the average Squared-Euclidean distance over control
signals between examples is above a threshold, then the Crowdsource Supervisor is not asked to provide additional examples.

\noindent \textbf{Human Expert Supervisor} The final supervisor, $S_3$ is the Human Expert supervisor, who is capable of
achieving high cumulative reward but is a limited resource. An Human Expert Supervisor in this case is a PhD student in
machine learning and robotics, to which we assign a cost of $C_3=1.0$ to signify a higher pay rate than the previous supervisor. The Human Expert Supervisor uses the same
interface as the Crowd-Sourced supervisors, shown in Fig. \ref{fig:overlays}, to provide examples to the robot.

An expert supervisor can utilize a variety of knowledge about the physical limitations of the robot and environment,
joint limits and experience in how certain objects might behave under force. Furthermore, the expert supervisor might
have an intuition for how training examples could lead to better training of the robot's policy $\pi_\theta$.

@@

\includegraphics{f_figs/binary_segment.eps}

\caption{\footnotesize Example of how the binary mask applied to each RGB channel affects the input data. As can be seen
it reduces the range of each channel's pixel value from the range of [0,255] to [0,1], increasing robustness to small
lighting condition changes.  }

\label{fig:b_seg}
\end{figure}

\caption{\footnotesize  Shown above is a Zymark robot. The robot consists of an 3DOF arm in a planar workspace. It is able to extend its arm and rotate about a fixed base. The robot can also open and close its gripper.}

@@

We discuss our experimental setup and test the performance of using a supervisor hierarchy versus a baseline approach
with one supervisor. We then evaluate the quality the Crowd-Source supervisors.

\subsection{Experimental Setup}
We work with a Zymark robot to perform a grasping in clutter task. The robot, shown in Fig. \ref{fig:robot}, has a 3
dimensional internal state of base rotation, arm extension and gripper opening width. The robot is commanded via position 
control with a tuned PID controller. We used
relative state control because this enabled us to easily enforce stay out zones for safety
and to register control signals to the labeling interface in Fig. \ref{fig:overlays}. We utilize the two main rotational joints of the
robot as degrees of freedom which are controlled by a neural network policy $\pi_{\theta}$ trained on image data taken by
an overhead Logitech C270 camera. Examples of images from the camera can be seen in Fig. \ref{fig:teaser}.

We consider objects made of Medium Density Fiberboard with an average 4" diameter and 3" in height. The objects used to form clutter are
painted red while the goal object is a yellow cylinder. The robot workspace consists of a disk region which is
surrounded by an elevated plate constraining the objects to the workspace and prohibiting them from being swept off
the workspace, thus adding to the difficulty of the task.

Our policy $\pi_{\theta}$ is represented as a deep neural network, which was trained using
TensorFlow~\cite{tensorflow2015-whitepaper}. Our network architecture consists of 1 convolutional layer with 5 channels
and filters with size 11x11, a fully connected layer with an output of 128 dimensions and a final layer that maps to a
four dimensional control signal. We used ReLus to separate the different layers and a final tanh on the output to scale
the output between -1 and 1. Each policy runs for a total of $T=100$ timesteps.

The control examples were scaled between 1 and -1 for each dimension independently. To be robust to lighting and reduce
the dimensionality of the problem, we applied a binary mask to each channel of the 250x250 RGB video frames setting
values above 125 to one and 0 otherwise. Each channel is shown in Fig. \ref{fig:b_seg}.
The policy $\pi_\theta$ outputs delta position control signals for a given input video frame.
Originally we considered also controlling two additional degrees of freedom of the arm: a turn-table motor controlling
the rotation of the disc workspace and the single degree of freedom of the robot gripper. However, in initial
experiments controlling the turn table proved unintuitive and was rarely used by human supervisors and the gripper degree of freedom was only used at the end of a policy. As a result, we labeled these output degrees of freedom with zero and instead automatically closed the gripper
at the final T=100 timestep. The joint controls were limited to $\pm 15$ degrees for rotation and $1$ cm for the
extension degree of freedom.

To determine our network architecture we performed a search over 40 different architectures trained after 400 iterations
with a batch size of 200. The set of architectures consisted of different network architectures in terms of
convolutional layers, fully connected layers and size of each one as well as different gradient descent momentum
terms used in learning, and weight initialization schemes. In finding an architecture, we trained all networks on a dataset of 6K images labeled with the MPIO Supervisor on a Nvidia Tesla K40 GPU, which is able to train each network in an average of 10 minutes.

>>>>

\title{Robot Grasping in Clutter:\\
 Using a Hierarchy of Supervisors for Learning from Demonstrations}

\author{Michael Laskey$^1$, Jonathan Lee$^1$, Caleb Chuck$^1$, David Gealy$^1$, Wesley Hsieh$^1$, Florian T. Pokorny$^1$,\\
 Anca D. Dragan$^1$, and Ken Goldberg$^{1,2}$% <-this % stops a space
\thanks{$^1$ Department of Electrical Engineering and Computer Sciences; {\small \{mdlaskey, jonathan\textunderscore lee, calebchuck, dgealy, wesleyhsieh, ftpokorny, anca\}@berkeley.edu} }%
\thanks{$^2$ Department of Industrial Engineering and Operations Research; {\small goldberg@berkeley.edu}}%
\thanks{$^{1-2}$ University of California, Berkeley;  Berkeley, CA 94720, USA}%
}
\begin{document}

@@

\begin{abstract}
For applications such as Amazon warehouse order fulfillment, robots must grasp a desired object amid clutter: other objects that block direct access. This can be difficult to program explicitly due to uncertainty in friction and push mechanics and the variety of objects that can be encountered. Deep Learning networks combined with Online Learning from Demonstration (LfD) algorithms such as DAgger and SHIV have potential to learn robot control policies for such tasks where the input is a camera image and system dynamics and the cost function are unknown.  To explore this idea, we introduce a version of the grasping in clutter problem where a yellow cylinder must be grasped by a planar robot arm amid extruded objects in a variety of shapes and positions. To reduce the burden on human experts to provide demonstrations, we propose using a hierarchy of three levels of supervisors: a fast motion planner that ignores obstacles, crowd-sourced human workers who provide appropriate robot control values remotely via online videos, and a local human expert. Physical experiments suggest that with a fixed budget of 160 expert demonstrations, using the hierarchy of supervisors can increase the probability of a successful grasp (reliability) from $55\%$ to $90\%$.

@@

\section{Introduction} 
As illustrated by the recent Amazon Picking Challenge at ICRA 2015, the grasping in clutter problem, where a robot needs
to grasp an object that might be occluded by other objects in the environment poses an interesting challenge to robotic
systems. This problem is relevant to industrial applications such as warehouse shipping operations and flexible manufacturing in semi-structured environments. One fundamental approach to grasping in clutter is the analytic model driven approach~\cite{bicchi2000robotic},
where the interaction dynamics between the robot and obstacles are formulated analytically. However, modeling all the 
physical properties of interaction poses a highly challenging problem due to uncertainty in modeling parameters such as
inertial properties and friction.

@@

\begin{figure}
\includegraphics[width=0.5\textwidth]{f_figs/teaser_h.eps}
\caption{
    \footnotesize
Three policy roll-outs on a Zymark 3-DOF Robot of a fully trained grasping in clutter policy (one per row, left to
right) which was trained using a hierarchy of three supervisors consisting of a motion planning algorithm, crowd-sourcing and a human expert. 
Red shapes indicate clutter objects and the robot is trained to reach the yellow cylinder. The trained manipulation
policy is represented as a deep neural network that receives as input an image of the scene and outputs a change in
state position. The resulting policy learns to sweep away clutter objects to reach the goal object. }
\vspace*{-20pt}
\label{fig:teaser}
\end{figure}

@@

Our approach is based on Online Learning from Demonstrations where a robot iteratively learns a policy and is
provided feedback on the current policy roll out by a supervisor~\cite{grollman2007dogged,ross2010efficient,ross2010reduction}. 
We build on, DAgger, an online LfD algorithm which at each iteration, computes a policy based on prior demonstrations,
and then rolls out that policy. A supervisor then provides control signals as feedback on the current policy
and new state/control examples are aggregated with the prior examples for the next iteration. DAgger and related algorithms have been applied in a wide range of applications, from quadrotor flight, natural language and Atari games~\cite{NIPS2014_5421,duvallet2013imitation,ross2013learning}. 
Ross et al. showed that DAgger, under a no-regret assumption, can be guaranteed to deviate from the supervisor's policy with an error
at most linear in the time horizon for the task~\cite{ross2010reduction}.

One drawback is that DAgger imposes a substantial burden on the supervisor, who must label all states that the robot
visits during training.  Previously a single expert supervisor has been considered 
~\cite{ross2010efficient,laskeyshiv,ross2010reduction,ross2013learning,duvallet2013imitation}.

We  propose to instead
utilize a hierarchy of supervisors  to incrementally
bootstrap the learning process, as opposed to utilizing an expensive
expert supervisor from scratch. Thus, at the lowest level of the hierarchy, we use a motion planner on a simplified
version of the grasping in clutter problem that ignores ambient obstacles. As the next supervisor in the hierarchy, 
we consider crowd-sourced workers on Amazon Mechanical Turk and finally the robot is trained with a PhD student in
robotics, who is considered an expert human supervisor. Experiments suggest that with a fix budget of 160 expert demonstrations leveraging a hierarchy of supervisors can increase reliability from $55\%$ to $90\%$ on a test set of unknown object configurations. 
%Learning can be bootstrapped with a sequence of increasingly skilled supervisors. In our grasping in clutter example, the robot spends a large portion of the time learning how to go towards the goal object. Analytical techniques such as forward kinematics, template matching and motion planning are readily available to provide examples in these parts of the state space.

@@

\section{Related Work}
Below, we summarize related work in Robotic Grasping in Clutter, the Online LfD setting and Curriculum learning.

\noindent \textbf{Robotic Grasping in Clutter}
Robotic grasping is a well-established research topic in robotics that has been studied for several
decades~\cite{bicchi2000robotic}. A significant amount of prior work focuses on planning grasps given a known object.
However, in unstructured environments clutter poses a significant challenge for reaching the planned grasp
~\cite{katz2008can}.

Prior work has studied the problem of manipulating objects
by performing pushing operations~\cite{mason1986mechanics}.  Cosgun et al.~\cite{cosgun2011push} and King et al. \cite{kingnonprehensile} consider the problem of planning a series of push operations that move an object to a
desired target location. We are interested in reaching a desire goal object, not how to move an object to a specific pose.

Additionally prior work has studied the use of hierarchical approaches for motion planning amid movable obstacles ~\cite{stilman2007manipulation,van2009path}. The approach is to use sampling-based methods to compute a high-level plan to move objects our of the way and get to a goal location. Dogar and Srinivasa applied this approach to push-grasping in clutter that plans a trajectory towards a grasp by maintaining a set of movable objects~\cite{dogar2011framework}. Our approach could be potentially integrated with a high level planner for more advance problems, where removing objects from the environment is needed.

Dogar et al. proposed a physics-based grasp planning approach that pre-computes and caches interactions with obstacles in the environment, which allows for fast real evaluation for a planner~\cite{dogar2012physics}. However, it does not account for inter-object interactions, which can be significant in cluttered environments. A supervisor could potentially impart an intuition for inter-object interaction while training the robot. Kiteav et al. planned a trajectory in a physics simulator using LQG based controllers
\cite{kitaevphysics} to reach a goal object surrounded by movable obstacles. They demonstrated that leveraging knowledge of object dynamics can lead to higher success than only motion planning.  However, for unknown objects it can be difficult to know parameters such as mass and friction coefficient, which are important for simulation.

Leeper et al. ~\cite{leeper2012strategies} used a human operator for assistance
to guide the robot through clutter with the objective of grasping a target object. However, the robot required the human
to be present at all times and did not attempt to learn to operate autonomously. We are interested in a data-driven
approach that only queries a supervisor at training time and  can operate autonomously thereafter.

Prior work has addressed integrated perception and grasping in clutter where the objective is to
grasp objects in an unorganized pile~\cite{pinto2015supersizing,nieuwenhuisen2013mobile}, but these methods do not
specifically aim to grasp a single target object in clutter. We train a robot specifically to move towards a goal object and treat other objects as clutter.

A model-free approach to robotic manipulation is Guided Policy Search~\cite{levine2015end}. However, this assumes a
known low-dimensional state representation to both estimate dynamics and apply an LQG controller. In the grasping in clutter
domain, it can be hard to specify such a low dimensional representation due the dependence on the objects' shape.

@@

\noindent\textbf{Reducing Supervisor Burden in Online LfD} 
Active learning approaches to reducing supervisor burden only ask for supervision when the robot is uncertain about the
correct control to apply. Traditional active learning techniques like query-by-committee and uncertainty sampling have
been utilized for this purpose \cite{chernova2009interactive,judah2011active,grollman2007dogged}
Kim et al. demonstrated that due to the non-stationarity of the distribution of states encountered during
learning, the traditional active learning techniques may not be suitable.
Thus the use of novelty detection was proposed~\cite{kim2013maximum}. Laskey et al. introduced SHIV, using an active
learning approach tailored to high dimensional and non-stationarity state distributions and a modified version of the
One Class SVM classifier. This reduced the density estimation problem to a 
simpler regularized binary classification~\cite{laskeyshiv}.

However, all of these works focus on reducing the duration of the demonstration an expert needs to provide. We focus on reducing the number of demonstrations the expert needs to provide, not the duration.

@@

\section{Robot Grasping in Clutter}\label{sec:sys}
 We consider a robot grasping an
object in a cluttered environment. The robot's goal is to grasp a  target, or goal, object in the presence of extruded
 objects obstructing the path towards the goal object. Kiteav et al. demonstrated that applying only a motion planner to this problem is not as successful as incorporating knowledge of object dynamics \cite{kitaevphysics}. However, since contact dynamics can be difficult to model without  information such as friction coefficient and mass \cite{kitaevphysics,kingnonprehensile}, we do not assume knowledge of explicit object or dynamics models and instead learn a grasping policy directly from demonstrations. We consider the following robot system, three supervisors $S_1, S_2, S_3$ and neural network policy architecture:

\noindent \textbf{Robot System}
The robot, shown in Fig. \ref{fig:robot}, has a 3
dimensional internal state of base rotation, arm extension and gripper opening width. The state space of the environment, $\mathcal{X}$, is captured by  an overhead Logitech C270 camera, which is positioned to capture the workspace that contains all cluttered objects, the goal object and the robot arm. Examples of images from the camera can be seen in Fig. \ref{fig:teaser}. The robot is commanded via position 
control with a  PID controller. Similar to \cite{laskeyshiv}, the controls, $\mathcal{U}$, to the robot are bounded changes in the internal state, which allows for us to easily register control signals to the demonstrations provided by supervisors as opposed to torque control. The control signals for each degree of freedom are continuous values with the following ranges: base rotation, $[-15^\circ,15^\circ]$, arm extension $[-1,1]$. The units are degrees for base rotation and centimeters for arm extension. The precision of control signal is $0.001$ for each degree of freedom. As opposed to unsupervised learning, where discretization of controls helps reduce computational complexity. In supervised learning, or regression, it is common to use a high level of precision for control signals ~\cite{levine2015end, laskeyshiv,kim2013maximum}.

The robot receives feedback from a supervisor by first executing a trajectory that has a time horizon, $T$, or $T=100$. The trajectory, which is composed of $100$ states, or images captured by the camera, is then given to a supervisor, who provides a demonstration. A demonstration is defined as the supervisor providing  the control they would apply if it was in the robot's current state, for each state in the trajectory. The robot then uses these demonstrations  in an approach similar to supervisor learning,  described in Sec. \ref{sec:PS}, to  update its current manipulation policy.

\caption{\footnotesize  Shown above is a Zymark robot. The robot consists of a 3DOF arm in a planar workspace. It is able to extend its arm and rotate about a fixed base. The robot can also open and close its gripper.}
\vspace*{-20pt}

\noindent \textbf{MPIO: Motion Planner Ignoring Obstacles Supervisor} Supervisor, $S_1$, is a first order motion planner that computes
control signals for the robot to reach the goal object in a straight line, ignoring the presence of obstacles. We refer to this supervisor as Motion Planner  Ignoring Obstacles (MPIO). Our
method employs template matching to identify the goal object in the image and uses the forward dynamics of the robot to
compute the relative change in direction the robot should apply as a control. The template matching is implemented in
OpenCV and uses the normalized cross-correlation filter~\cite{opencv_library}. This supervisor is designed to just provide an initial improvement of a random neural network policy.

\caption{\footnotesize  The interface AMT workers see for providing feedback to the robot for the grasping in clutter task. The pink overlay indicates the desire desire control, which is a bounded change in internal state, the robot should apply. Then AMT workers can use their intuition for how objects respond to force to provide examples of how the robot should behave. On the left side is an example of a robot state and on the right side is an example a human supervisor would provide via a Computer Mouse.}
\vspace*{-20pt}
\label{fig:overlays}
\end{figure}

\noindent \textbf{Crowd-Sourced Supervisor} Supervisor, $S_2$, uses a crowd source service, called Amazon
Mechanical Turk (AMT). The AMT platform makes readily available thousands of human workers that can provide 
supervision for \$0.10 per demonstration. The time to provide a demonstration to the robot takes 50s, since the robot trial is slowed down to a half second per time-step in the trajectory.

In order to have the AMT workers provide demonstrations, we designed the supervision interface shown in Fig. \ref{fig:overlays}. The interface displays a video of a trajectory in the image state space and allows the human supervisors to command an overlay visualization of the robot arm to
demonstrate the correct control the robot should be applied. The interface is controlled via a mouse, which when held down a robot visualization appears and can be dragged to the desired control (or change in state) the robot should apply. The desired control is bounded by the range in controls listed above.

We  designed a tutorial for the Crowd-Sourced Supervisor. We first describe the learning task to them as a
robot that is trying to reach a yellow cylinder and needs their help learning how to get it. In a tutorial, they are then trained
to perform designated motions with a virtual robot, to help them understand  the robot's kinematics. We additionally
provide a video of an expert providing corrections on three robot trajectories. We instruct the Crowd-Sourced
Supervisor to only provide a control when they are confident. If a state in the demonstration does not receive a label that state is not added to the training set.

To help ensure quality, we provide all Crowd-Sourced Supervisors with the same trajectory first and compare their
demonstration against a demonstration of a Human Expert Supervisor. If the average Squared-Euclidean distance over control
signals between demonstrations is above a threshold, then the CrowdSource Supervisor is not asked to provide additional demonstrations. The threshold is set with the intention to only remove  AMT workers, who provide arbitrary demonstrations, no demonstrations or possibly adversarial demonstrations.

\noindent \textbf{Expert Supervisor} Supervisor, $S_3$ is the  Expert Supervisor, who is capable of
a better understanding of the problem domain but is a limited resource. An Expert Supervisor in this case is a PhD student in
machine learning and robotics. The Expert Supervisor uses the same
interface as the Crowd-Sourced supervisors, shown in Fig. \ref{fig:overlays}, to provide examples to the robot.

An Expert Supervisor can utilize a variety of knowledge about the physical limitations of the robot and environment,
joint limits and experience in how certain objects might behave under force. Furthermore, the Expert Supervisor might
have an intuition for how training examples could lead to better training of the robot.

\noindent \textbf{Neural Network Policy Architecture}
In Online LfD, a  robot is trained by learning a policy, or function mapping state space $\mathcal{X}$ to control space $\mathcal{U}$. Commonly, a policy is a specific function in some function class such as linear regression, kernelized ridge regression, or a neural network. To handle the high dimensional image space of the problem, we are interested in representing the robot's policy as a deep neural network. Deep learning can be advantageous because it has the potential to learn features relevant for manipulation~\cite{levine2015end,pinto2015supersizing}. Furthermore as opposed to kernel based methods, neural networks readily support online updates (i.e. the ability to add more demonstrations without having to retrain on previous demonstrations)~\cite{scholkopf2002learning}, which can be important when switching supervisors in the hierarchy.

To facilitate training the neural network, we scaled the controls  between 1 and -1 for each dimension independently, which is common for training ~\cite{tensorflow2015-whitepaper}. To be robust to lighting and reduce
the dimensionality of the problem, we applied a binary mask to each channel of the 250x250 RGB images setting
values above 125 to one and 0 otherwise.
The policy  outputs a 4 dimensional control signals, or delta state positions, for a given input image or state. The network also has the ability to control the turn-table motor controlling the rotation of the disc workspace and the single degree of freedom of the robot gripper. However, we do not use these controls in experiments and in the training data set those controls to $0$.

 Our network architecture was designed as follows. First, to work with image data we used a convolutional layer with 5 channels and 11x11 filters. Then we added a Rectified Linear Unit (i.e. $\mbox{max}(0,x)$) or ReLu,  to add a non-linearity between layers. ReLus have been shown to allow for faster training than other non-linear separators~\cite{krizhevsky2012imagenet}. After the non-linearity we added a fully connected layer, or a weight matrix with an out dimension of 128. Then  another ReLu  followed by a weight matrix that maps to the 4 dimensional output. We place a final $\mbox{tanh}$ function on the output, which  enforces the output is between $-1$ and $1$.

To determine parameters of the network architecture described we performed a search over 30 different architectures trained after 400 iterations
with a batch size of 200. The set of architectures consisted of different network architectures in terms of
convolutional layers, filter size,  fully connected layers and output dimension of each layer. In finding an architecture, we trained all networks on a dataset of 6K state/control pairs from the MPIO Supervisor on a Nvidia Tesla K40 GPU, which is able to train each network in an average of 10 minutes.  All networks were trained using Stochastic Gradient Descent with Momentum in TensorFlow ~\cite{tensorflow2015-whitepaper}. Momentum is a method to control the magnitude of the gradient based on how large previous gradients were. We used a gradient step size,or learning rate of $0.01$ and a momentum term of $0.9$.

\section{Online Learning From Demonstrations}\label{sec:PS}
Given a collection of increasingly skilled supervisors $S_1, \ldots, S_M$, the goal of this work is to learn a
policy that closely matches that of the most skilled supervisor $S_M$ while minimizing the overall number of queries to the more skilled supervisors.

\noindent\textbf{Assumptions and Modeling Choices } 
We assume a known state space and set of controls. We also assume access to a robot or simulator, such that we can sample from the state sequences induced by a sequence of controls. Lastly, we assume access to a set of supervisors who can, given a state, provide a control signal label. We additionally assume the supervisors can be noisy and imperfect.

@@

This sub-problem is a supervised learning problem, which we solve with a deep neural network. Other approaches such as
kernel based regression can also be considered~\cite{scholkopf2002learning}.

@@

@@

@@

\subsection{Experimental Setup}
For the grasping in clutter task, we consider objects made of Medium Density Fiberboard with an average 4" diameter and 3" in height. The objects used to form clutter are red extruded polygons while the goal object is a yellow cylinder.  The robot workspace, which is green, consists of a  30" disk region which is
surrounded by an elevated plate constraining the objects to a ring and prohibiting them from leaving the camera's field of view.

To test the performance of each robot policy, we created a test set composed of 20 different configurations each containing
objects that were not in the training set.  The training objects and test
objects introduced during testing are shown in Fig. \ref{fig:shape_set}. The test set configurations varied by placing
test objects from Fig. \ref{fig:shape_set} with objects we trained on in similar configurations. Examples of training and test configurations are shown in Fig. \ref{fig:suc_meas}.  During training and testing, we manually place the objects in configurations. However, a hardware mechanism that moves the objects around, such as a pre-defined sweeping motion from the robot arm, could be used in future work. We measure success by whether the object was in the gripper at the final timestep. We define reliability or $\rho$ as the percentage of successful configurations.

Per iteration of Hierarchical DAgger, we collect 20 trajectories on different training configurations and then have a supervisor provide 20 demonstrations. We do this to sample a variety of configurations with the current policy before updating the weights. Thus 100 robotic trials correspond to 5 iterations of DAgger.

\subsection{Three Types of Supervisors}
